Public Opinions on Sexual Education in Public Schools: An Analysis of Political, Educational, and Generational Influences in the United States from 1972 to 2022

### 2024-03-12 paper/paper.qmd
Update Scripts and paper

GSS_metadata <- read.dct("../data/raw_data/GSS.dct")
GSS_ascii <- read.dat("../data/raw_data/GSS.dat", GSS_metadata)
attr(GSS_ascii, "col.label") <- GSS_metadata[["ColLabel"]]
data <- GSS_ascii
```

>>>>

GSS_metadata <- read.dct("../data/GSS.dct")
GSS_ascii <- read.dat("../data/GSS.dat", GSS_metadata)
attr(GSS_ascii, "col.label") <- GSS_metadata[["ColLabel"]]
data <- GSS_ascii
```
